---
title: "Core Utils for Mass Spectrometry Data"
author:
- name: MsCoreUtils Package Maintainers
package: MsCoreUtils
output:
  BiocStyle::html_document:
    toc_float: true
bibliography: Features.bib
vignette: >
  %\VignetteIndexEntry{Core Utils for Mass Spectrometry Data}
  %\VignetteEngine{knitr::rmarkdown}
  %%\VignetteKeywords{Mass Spectrometry, MS, MSMS, Proteomics, Metabolomics, Infrastructure, Quantitative }
  %\VignetteEncoding{UTF-8}
---

```{r style, echo = FALSE, results = 'asis'}
BiocStyle::markdown()
```


# Introduction

The `MsCoreUtils` package low-level functions for mass spectrometry
data and is independent of any high-level data structures. These
functions include mass spectra processing functions (noise estimation,
smoothing, binning), quantitative aggregation functions (median
polish, robust summarisation, ...), missing data imputation, data
normalisation (quantiles, vsn, ...)  as well as misc helper functions,
that are used across high level data structure within the R for Mass
Spectrometry packages.

For a full list of function, see 

```{r}
library("MsCoreUtils")
ls(pos = "package:MsCoreUtils")
```

or the [reference
page](https://rformassspectrometry.github.io/MsCoreUtils/reference/index.html)
on the package webpage.


# Examples

The functions defined in this package utilise basic classes with the
aim of being reused in packages that provide a more formal, high-level
interface.

As an examples, let's take the `robustSummary()` function, that
calculates the robust summary of the columns of a matrix:

```{r}
x <- matrix(rnorm(30), nrow = 3)
colnames(x) <- letters[1:10]
rownames(x) <- LETTERS[1:3]
x
robustSummary(x)
```

This function is typicall to be used to summarise peptide quantitation
values into protein intensities[^robuststum]. This functionality is
available in the
[`MSnbase::combineFeatures()`](http://lgatto.github.io/MSnbase/reference/combineFeatures.html)
function for `MSnSet` objects and the
[`Features::aggregateFeatures()`](https://rformassspectrometry.github.io/Features/reference/Features-aggregate.html)
function for `Features` objects.


[^robuststum]: See Sticker *et al.* Robust summarization and inference
    in proteome-wide label-free
    quantification. https://doi.org/10.1101/668863.


# Session information {-}

```{r sessioninfo, echo=FALSE}
sessionInfo()
```

